The Cost of Exclusion: Political Discrimination and Trust Deficits in the European Union

### 2025-07-11 article/main.tex
Exhanging dissonance for divergence

While Europe has historically exhibited lower levels of affective polarization and declining partisan identification, recent studies suggest the presence of partisan hostility and negative feelings driven by factors such as ideological distance, perceived party threats, and regional tensions. Yet, evidence on longitudinal trends is still inconclusive. Scholars continue to emphasize the need for improved measurements and long-term data to determine whether affective polarization is indeed increasing across European democracies \textcite{wagner_affective_2024}.

@@

Amid this environment, institutional trust is often viewed as a background condition for democratic stability. However, trust plays a more active and central role—it serves as a fundamental mechanism through which political systems gain legitimacy and foster public compliance. A robust body of literature supports the idea that institutional trust enhances democratic resilience, encouraging civic engagement and reinforcing institutional performance \parencite{marien_measuring_2011, devine_stability_2024}.

@@

To overcome this challenge, we employ matching methods and sensitivity analyses to estimate the causal effect of D/H experiences on institutional trust. Our analysis draws on a novel dataset from the EUROVOICES project, a general population survey carried out by the World Justice Project across all 27 European Union Member States. The dataset offers statistically representative coverage across 110 subnational regions, providing an unprecedented level of geographic and demographic granularity.

@@

However, the effect of discrimination is not uniform—it varies depending on the individual's political alignment and sense of political dissonance. We show that individuals who experience discrimination and simultaneously feel ideologically out of place experience the largest declines in institutional trust. Although trust decreases across the board, the magnitude of the effect differs significantly between politically aligned and non-aligned individuals. Among those not aligned with the incumbent party, experiencing D/H is associated with a 20\% reduction in trust, compared to a 14\% reduction for aligned individuals.

Furthermore, among individuals with low political dissonance, D/H experiences do not significantly affect trust if the individual is politically aligned. In contrast, non-aligned individuals in this group experience an 18\% drop in trust. On the other hand, for individuals experiencing high political dissonance, trust erosion remains high—between 18\% and 21\%—regardless of political alignment. Notably, the difference between aligned and non-aligned individuals in this group is not statistically significant.

@@

Importantly, the effects of political discrimination may not be uniform or isolated from the complexities of other political phenomena. In contexts of rising affective polarization, where political identities become emotionally charged and intergroup hostility intensifies \parencite{iyengar_origins_2019, mccoy_polarization_2018}, perceptions of fairness and legitimacy are increasingly filtered through partisan lenses.

In this context, we argue that the effects of experiencing political discrimination or harassment on institutional trust are differentiated depending on two key factors: political dissonance and political alignment.

We define political dissonance as the psychological and emotional tension experienced by individuals who perceive a mismatch between their political identity and the dominant political climate or institutional stance \parencite{lelkes_limits_2017, federico_ideological_2012}. Unlike affective polarization, which operates at the societal level, political dissonance is individually experienced and marked by feelings of alienation, frustration, and disillusionment.

Political dissonance is exacerbated in polarized societies where outgroup hostility, moral condemnation, and dehumanization are common \parencite{iyengar_fear_2015}. This intensifies the emotional toll of political discrimination and heightens perceptions of institutional betrayal \parencite{hetherington_why_2015}. In turn, this reduces trust and discourages political participation \parencite{michelson_corrosive_2003, lelkes_limits_2017}.

@@

\emph{\textbf{\small
H2: People with different levels of political dissonance respond differently to political discrimination, leading to varying degrees of declining trust in public institutions.
}}

The second mechanism concerns the politicization of institutional perception—the tendency to evaluate institutions based not on their procedures or performance, but on perceived political alignment. In highly polarized contexts, even neutral institutions are judged through partisan filters \parencite{rogowski_how_2016, druckman_what_2019}, leading to a fragmentation of legitimacy. Trust becomes conditional on whether individuals perceive institutions as aligned with their own political views.

In such environments, those who experience political discrimination may interpret institutions—even those uninvolved in the discrimination—as biased or complicit. Conversely, individuals aligned with dominant political forces may continue to express trust in the same institutions, despite evidence of exclusion.

\emph{\textbf{\small
H3: Individuals who experience political discrimination will exhibit different patterns of institutional (dis)trust based on their political alignment.
}}

Figure \ref{fig:0} presents our conceptual framework, linking political discrimination, affective polarization, and institutional trust through sequential and interactive pathways. At its core is the idea that political discrimination functions as an initial grievance—eroding perceived fairness and inclusion, and in turn diminishing trust in institutions.

@@

Ultimately, the interaction between political discrimination and polarization does not produce a uniform decline in trust. Instead, it fragments perceptions of legitimacy. Those who feel politically marginalized are more likely to view institutions as biased or adversarial, while those who feel politically represented may retain confidence. These mechanisms reinforce one another, compounding democratic disaffection, deepening polarization, and threatening the foundations of pluralistic governance.

@@

Finally, as displayed in Table \ref{table:1}, the survey not only collects important demographic data but it also asks respondents key political traits such as their interest in politics, vote intention, and it also asks people to rate their political ideology from 0 to 10, where 0 is associated with a far left ideology and 10 is associated with a far right ideology.

@@

The main objective of this study is to examine whether experiencing discrimination or harassment (D/H experiences)\footnote{Throughout the remainder of this document, political discrimination or harassment will be referred to as D/H experiences or events.} due to political opinions has a causal effect on trust in political institutions. However, a fundamental challenge in causal inference is that assessing the causal effect of these experiences would require observing both potential outcomes in the same individual—those who experienced a D/H event and those who did not. Since we never observe both potential outcomes for any individual, we must infer the effects of political discrimination and harassment by comparing average trust levels between those who experienced such events and those who did not.

@@

Finally, we investigate the mechanisms through which political discrimination and harassment affect trust in political institutions. We explore two potential pathways: political dissonance and political alignment.

Regarding political polarization, we hypothesize that individuals who experience D/H events may become more politically polarized, which in turn could lead to lower levels of trust in political institutions. To test this hypothesis, we include a measure of political dissonance in our regression model and assess its interaction with the D/H event variable..

%and assess the transmission mechanism using the mediation analysis proposed by Imai et al. (2011) and Imai and Yamamoto (2013).\footnote{We use the mediation R package developed by Tingley et al. (2014) for the practical implementation of this framework.}

%The mediation analysis follows a two-step process. First, we examine how D/H experiences affect political polarization (see Equation \ref{eq:2}). Second, we analyze how both D/H experiences and political polarization jointly influence trust in political institutions (see Equation \ref{eq:3}). We measured political polarization at the individual level using a measure of political conformity/dissonance based on the political ideologies of the respondents. This measure is calculated as the square of the difference between the respondent's political ideology and the average political ideology of the country.\footnote{It is important to note that we use the full study sample to estimate the average political ideology of the country, rather than the matched sample. We believe that using the full representative country sample captures the true distance between the respondent's political ideology and the average political ideology of the country.}

% \begin{equation}
% \label{eq:2}
% M_{ic} = \alpha + \phi X_{ic} + \mathbf{Z}_{ic}'\mathbf{\beta} + \gamma_c + \epsilon_{ic}
% \end{equation}
% \begin{equation}
% \label{eq:3}
% Y_{ic} = \alpha + \delta X_{ic} + \rho M_{ic} + \mathbf{Z}_{ic}'\mathbf{\eta} + \lambda_c + \mu_{ic}
% \end{equation}

% Where:
% \begin{itemize}
%   \item \( Y_{ic} \): political trust for individual \( i \) in region \( c \)
%   \item \( X_{ic} \): D/H event (1 = treated, 0 = control)
%   \item \( M_{ic} \): political dissonance for individual \( i \) in region \( c \)
%   \item $\phi$, $\delta$, and $\rho$: coefficients of interests
%   \item \( \mathbf{Z}_{ic} \): vector of covariates
%   \item $\mathbf{\beta}$ and $\mathbf{\eta}$: coefficient vectors for covariates
%   \item $\gamma_c$ and $\lambda_c$: region fixed effects
%   \item $\epsilon_{ic}$ and $\mu_{ic}$: error terms
% \end{itemize}

% After fitting these models, we use bootstrapping to estimate causal effects under counterfactual scenarios. In each simulation, we compare predicted trust levels between two scenarios: experiencing D/H events versus not experiencing them, while allowing political dissonance to adjust to its expected level under each condition. Averaging across simulations yields the average causal mediation effect (ACME), which captures the indirect effect through polarization, and the average direct effect (ADE), which captures the remaining direct impact.

Regarding politcal alignment, we hypothesize that there is heterogenous effects between individuals that are politically aligned with the incumbent party and those who are not. To test this hypothesis, we include a measure of political alignment with the incumbent party in our regression model (see Equation \ref{eq:4}) and assess its interaction with the D/H event variable.

@@

  Where:
  \begin{itemize}
    \item \( Y_{ic} \): political trust for individual \( i \) in region \( c \)
    \item \( X_{ic} \): D/H event (1 = treated, 0 = control)
    \item \( D_{ic} \): pathway (high political dissonance or political aligned) for individual \( i \) in region \( c \)
    \item \( \tau \): treatment effect (ATT)
    \item \( \delta \): pathway unilateral effect on Trust in Political Institutions Index
    \item \( \phi \): interaction effect between D/H event and political alignment with the incumbent party
    \item \( \mathbf{Z}_{ic} \): vector of covariates
    \item \( \mathbf{\beta} \): coefficient vector for covariates
    \item \( \gamma_c \): region fixed effects
    \item \( \varepsilon_{ic} \): error term
  \end{itemize}

@@

We wanted to further explore the relationship between political alignment and the effect of political discrimination and harassment on trust in political institutions. Given the results presented in the previous section, we consider the possibility that the heterogenous effects found in politically aligned individuals might be affected by their level of political dissonance. To answer this question, we further increased the level of disaggregation by estimating the effect of political discrimination and harassment on trust in political institutions for four different groups depending on their political alignment and their level of political dissonance.\footnote{The level of political dissonance was categorized in either high or low depending if the individual's measure was above or below the median of the full study sample, respectively.}

As Table \ref{table:8} shows, for individuals with a low level of political dissonance, experiencing a D/H event does not has any effect on their level of trust in political institutions if they are politically aligned with the incumbent party, while their counterparts that are not politically aligned experience a 18\% decrease in trust in political institutions.

On the other hand, for individuals with a high level of political dissonance, the effect remains high between 18\% and 21\% for both politically aligned and non-aligned individuals. Interestingly, the effect is not statistically different between the two groups.

@@

The first is political dissonance, which occurs when individuals feel ideologically misaligned with the dominant political climate. Our findings support the second hypothesis (H2): individuals who both experience political discrimination and feel ideologically out of place exhibit the most pronounced declines in trust. This sense of disconnection intensifies perceptions of exclusion, reinforcing the belief that the political system no longer represents them \parencite{mccoy_polarization_2018, iyengar_fear_2015}.

As dissonance increases, experiences of discrimination are no longer perceived as isolated events but as symptomatic of a broader political environment seen as hostile. This magnifies resentment, sharpens perceived injustice, and increases receptiveness to populist or anti-establishment narratives that portray institutions as fundamentally biased. In this way, affective polarization amplifies the emotional and psychological toll of exclusion, deepening distrust and weakening democratic attachment.

@@

This mechanism differs from dissonance in that it focuses not on ideological mismatch, but on a shift in how institutions are perceived. Rather than being viewed as impartial guarantors of democracy, institutions are interpreted as aligned with opposing political forces. For individuals who have experienced political discrimination, this cognitive shift is especially pronounced. Prior exclusion fosters suspicion, increasing the likelihood that institutional behavior is seen as adversarial or punitive.

@@

Taken together, these findings reveal a layered and interactive erosion of institutional trust in polarized political environments. Rather than operating through a single channel, the effects of political discrimination unfold through mutually reinforcing cognitive pathways. Political dissonance highlights the emotional and psychological costs of ideological alienation, while politicized perception reshapes how individuals interpret the role and legitimacy of institutions.

>>>>

While Europe has historically exhibited lower levels of affective polarization and declining partisan identification, recent studies suggest the presence of partisan hostility and negative feelings driven by factors such as ideological distance, perceived party threats, and regional tensions. Yet, evidence on longitudinal trends is still inconclusive. Scholars continue to emphasize the need for improved measurements and long-term data to determine whether affective polarization is indeed increasing across European democracies \parencite{wagner_affective_2024}.

@@

Amid this environment, institutional trust is widely recognized as a foundational condition for democratic stability. However, trust plays a more active and central role—it serves as a fundamental mechanism through which political systems gain legitimacy and foster public compliance. A robust body of literature supports the idea that institutional trust enhances democratic resilience, encouraging civic engagement and reinforcing institutional performance \parencite{marien_measuring_2011, devine_stability_2024}.

@@

To overcome this challenge, we employ matching methods and sensitivity analyses to estimate the causal effect of D/H experiences on institutional trust. Our analysis draws on a novel dataset from the EUROVOICES project, a general population survey carried out by \textcite{the_world_justice_project} across all 27 European Union Member States. The dataset offers statistically representative coverage across 110 subnational regions, providing an unprecedented level of geographic and demographic granularity.

@@

However, the effect of discrimination is not uniform—it varies depending on the individual's political alignment and level of ideological divergence. We show that individuals who experience discrimination and simultaneously feel ideologically out of place experience the largest declines in institutional trust. Although trust decreases across the board, the magnitude of the effect differs significantly between politically aligned and non-aligned individuals. Among those not aligned with the incumbent party, experiencing D/H is associated with a 20\% reduction in trust, compared to a 14\% reduction for aligned individuals.

Furthermore, among individuals with low ideological divergence, D/H experiences do not significantly affect trust if the individual is politically aligned. In contrast, non-aligned individuals in this group experience an 18\% drop in trust. On the other hand, for individuals displaying high ideological divergence, trust erosion remains high—between 18\% and 21\%—regardless of political alignment. Notably, the difference between aligned and non-aligned individuals in this group is not statistically significant.

@@

Importantly, the effects of political discrimination may not be uniform or isolated from the complexities of other political phenomena. In contexts of rising polarization, where political identities become emotionally charged and intergroup hostility intensifies \parencite{iyengar_origins_2019, mccoy_polarization_2018}, perceptions of fairness and legitimacy are increasingly filtered through partisan lenses.

This brings us to the concept of ideological polarization. According to \textcite{lelkes_limits_2017}, polarization can be understood in two distinct ways. First, as alignment, which refers to the extent to which party identification increasingly corresponds with ideological beliefs, and political attitudes become more internally consistent. Second, as divergence, defined as the extent to which ideological positions within a population spread apart, increasing the overall distance between opposing views. In this context, we argue that the effects of experiencing political discrimination or harassment on institutional trust are differentiated depending on two key factors: political alignment and ideological divergence.

According to \textcite{baldassarri_partisans_2008}, political polarization becomes threatening when it leads to alignment across multiple dimensions of social and political conflict, fostering exclusive group identities and solidifying interests into opposing factions. This argument raises the concern of a potentital politization of institutional perception—the tendency to evaluate institutions based not on their procedures or performance, but on perceived political alignment. In highly polarized contexts, even neutral institutions are judged through partisan filters \parencite{rogowski_how_2016, druckman_what_2019}, leading to a fragmentation of legitimacy. Trust becomes conditional on whether individuals perceive institutions as aligned with their own political views.

In such environments, those who experience political discrimination may interpret institutions—even those uninvolved in the discriminatory act—as biased or complicit. Conversely, individuals aligned with dominant political forces may continue to express trust in the same institutions, despite evidence of exclusion.

\emph{\textbf{\small
H2: Individuals who experience political discrimination will exhibit different patterns of institutional (dis)trust based on their political alignment.
}}

Simultaneously, ideological divergence can give rise to political dissonance—the psychological and emotional tension experienced by individuals who perceive a misalignment between their political identity and the dominant political climate or institutional stance \parencite{lelkes_limits_2017, federico_ideological_2012}.

Ideological divergence is exacerbated in polarized societies where outgroup hostility, moral condemnation, and dehumanization are common \parencite{iyengar_fear_2015}. This intensifies the emotional toll of political discrimination and heightens perceptions of institutional betrayal \parencite{hetherington_why_2015}. In turn, this reduces trust and discourages political participation \parencite{michelson_corrosive_2003, lelkes_limits_2017}.

@@

\emph{\textbf{\small
H3: People with different levels of ideological divergence respond differently to political discrimination, leading to varying degrees of declining trust in public institutions.
}}

Figure \ref{fig:0} presents our conceptual framework, linking political discrimination, ideological polarization, and institutional trust through sequential and interactive pathways. At its core is the idea that political discrimination functions as an initial grievance—eroding perceived fairness and inclusion, and in turn diminishing trust in institutions.

@@

Ultimately, the interaction between political discrimination and polarization does not produce a uniform decline in trust. Instead, it fragments perceptions of legitimacy. Those who feel ideologically marginalized are more likely to view institutions as biased or adversarial, while those who feel politically represented may retain confidence. These mechanisms reinforce one another, compounding democratic disaffection, deepening polarization, and threatening the foundations of pluralistic governance.

@@

Finally, as displayed in Table \ref{table:1}, the survey not only collects important demographic data but it also asks respondents key political traits such as their interest in politics, vote intention, and it also asks people to rate their political ideology from 0 to 10, where 0 is associated with a further left ideology and 10 is associated with a further right ideology.

@@

The main objective of this study is to examine whether experiencing discrimination or harassment due to political opinions has a causal effect on trust in political institutions (H1). However, a fundamental challenge in causal inference is that assessing the causal effect of these experiences would require observing both potential outcomes in the same individual—those who experienced a D/H event and those who did not. Since we never observe both potential outcomes for any individual, we must infer the effects of political discrimination and harassment by comparing average trust levels between those who experienced such events and those who did not.

@@

As outlined in our study hypotheses (H2 and H3), we also examine whether the effect of experiencing political discrimination or harassment varies according to an individual’s political alignment and ideological divergence. To test these hypotheses, we introduce interaction terms that allow us to assess whether the relationship between experiences of political discrimination and trust in political institutions is moderated by a third factor.

First, we include an interaction term between the D/H event variable and political alignment with the incumbent party. Political alignment is measured using a vote intention question included in the survey, which asked respondents who they would vote for if a general election were held in their country that weekend. Respondents who selected the incumbent party are categorized as politically aligned, while all others are considered unaligned (see Equation \ref{eq:4}).

Second, we introduce an additional layer of analysis by interacting the D/H event variable with a new measure of ideological divergence. To construct this variable, we follow a similar approach to \textcite{torcal_ideological_2022}, who capture ideological extremism as the distance between an individual’s ideological self-placement and the societal center—an operationalization of ideological polarization.\footnote{\textcite{torcal_ideological_2022} use this approach to measure ideological extremism, which they conceptualize as a manifestation of broader ideological polarization.}

Respondents were asked to place themselves on a scale from 0 to 10, where 0 represents a further left ideology and 10represents a further right ideology. We then calculate ideological divergence as the squared difference between each respondent's self-placement and the mean ideological position within their respective subnational region (see Equation \ref{eq:4}).

@@

  Where:
  \begin{itemize}
    \item \( Y_{ic} \): political trust for individual \( i \) in region \( c \)
    \item \( X_{ic} \): D/H event (1 = treated, 0 = control)
    \item \( D_{ic} \): pathway (high ideological divergence or political aligned) for individual \( i \) in region \( c \)
    \item \( \tau \): treatment effect (ATT)
    \item \( \delta \): pathway unilateral effect on Trust in Political Institutions Index
    \item \( \phi \): interaction effect between D/H event and political alignment with the incumbent party
    \item \( \mathbf{Z}_{ic} \): vector of covariates
    \item \( \mathbf{\beta} \): coefficient vector for covariates
    \item \( \gamma_c \): region fixed effects
    \item \( \varepsilon_{ic} \): error term
  \end{itemize}

@@

We wanted to further explore the relationship between political alignment and the effect of political discrimination and harassment on trust in political institutions. Given the results presented in the previous section, we consider the possibility that the heterogenous effects found in politically aligned individuals might be affected by their level of ideological divergence. To answer this question, we further increased the level of disaggregation by estimating the effect of political discrimination and harassment on trust in political institutions for four different groups depending on their political alignment and their level of ideological divergence.\footnote{The level of ideological divergence was categorized in either high or low depending if the individual's measure was above or below the median of the full study sample, respectively.}

As Table \ref{table:8} shows, for individuals with a low level of ideological divergence, experiencing a D/H event does not has any effect on their level of trust in political institutions if they are politically aligned with the incumbent party, while their counterparts that are not politically aligned experience a 18\% decrease in trust in political institutions.

On the other hand, for individuals with a high level of ideological divergence, the effect remains high between 18\% and 21\% for both politically aligned and non-aligned individuals. Interestingly, the effect is not statistically different between the two groups.

@@

The first is ideological divergence, which occurs when individuals feel ideologically misaligned with the dominant political climate. Our findings support the second hypothesis (H2): individuals who both experience political discrimination and feel ideologically out of place exhibit the most pronounced declines in trust. This sense of disconnection intensifies perceptions of exclusion, reinforcing the belief that the political system no longer represents them \parencite{mccoy_polarization_2018, iyengar_fear_2015}.

As divergence increases, experiences of discrimination are no longer perceived as isolated events but as symptomatic of a broader political environment seen as hostile. This magnifies resentment, sharpens perceived injustice, and increases receptiveness to populist or anti-establishment narratives that portray institutions as fundamentally biased. In this way, affective polarization amplifies the emotional and psychological toll of exclusion, deepening distrust and weakening democratic attachment.

@@

This mechanism differs from divergence in that it focuses not on ideological mismatch, but on a shift in how institutions are perceived. Rather than being viewed as impartial guarantors of democracy, institutions are interpreted as aligned with opposing political forces. For individuals who have experienced political discrimination, this cognitive shift is especially pronounced. Prior exclusion fosters suspicion, increasing the likelihood that institutional behavior is seen as adversarial or punitive.

@@

Taken together, these findings reveal a layered and interactive erosion of institutional trust in polarized political environments. Rather than operating through a single channel, the effects of political discrimination unfold through mutually reinforcing cognitive pathways. Ideological divergence highlights the emotional and psychological costs of ideological alienation, while politicized perception reshapes how individuals interpret the role and legitimacy of institutions.

### 2025-07-11 article/tabs/het_effects_dissonance.tex
Exhanging dissonance for divergence

\begin{table}[hbtp]
\centering
\caption{Effect of Political D/H Experiences on Institutional Trust by Level of Political Dissonance and Political Alignment}
\label{table:8}
\footnotesize
\vspace{2mm}
\begin{talltblr}[
label=none,
remark{Note} = {Table shows the estimated coefficient of having experienced political discrimination or harrasment (D/H) on the level of trust in political institutions for four different groups depending on their political alignment and their level of political dissonance. The estimation used the matched sample of 14,004 respondents, region fixed effects, demographic and political covariates, and clustered standard errors at the regional level. *, **, and *** represent statistical significance at $p < 0.05$, $p < 0.01$, and $p < 0.001$, respectively. Estimates shown in the table have been transformed using an exponential transformation to interpret them as a percentage change.},
remark{Source} = {Eurovoices General Population Poll 2024},
]
{                     
colspec={Q[l]Q[l]Q[c]Q[c]Q[c]Q[c]Q[c]},
colsep=4pt
}
\toprule
Pol. Diss. & Pol. Alignment & Estimate & $Pr(>|z|)$ & 95\% CI Lower & 95\% CI Upper & Visualization \\
\midrule
Low & Non-Incumbent & \num{ -0.180}*** & 0.000 & -0.209 & -0.149 & \includegraphics[width=0.47in, height=0.12in]{"viz/heteffects_dissonance_1.png"}\\
 & Incumbent & \num{-0.085} & 0.000 & -0.168 & 0.006 & \includegraphics[width=0.47in, height=0.12in]{"viz/heteffects_dissonance_2.png"}\\
High & Non-Incumbent & \num{-0.211}*** & 0.000 & -0.238 & -0.183 & \includegraphics[width=0.47in, height=0.12in]{"viz/heteffects_dissonance_3.png"}\\
 & Incumbent & \num{-0.179}*** & 0.000 & -0.241 & -0.111 & \includegraphics[width=0.47in, height=0.12in]{"viz/heteffects_dissonance_4.png"}\\
\bottomrule
\end{talltblr}
\end{table}

>>>>

\begin{table}[hbtp]
\centering
\caption{Effect of Political D/H Experiences on Institutional Trust by Level of Political Dissonance and Ideological Divergence}
\label{table:8}
\footnotesize
\vspace{2mm}
\begin{talltblr}[
label=none,
remark{Note} = {Table shows the estimated coefficient of having experienced political discrimination or harrasment (D/H) on the level of trust in political institutions for four different groups depending on their political alignment and their level of ideological divergence. The estimation used the matched sample of 14,004 respondents, region fixed effects, demographic and political covariates, and clustered standard errors at the regional level. *, **, and *** represent statistical significance at $p < 0.05$, $p < 0.01$, and $p < 0.001$, respectively. Estimates shown in the table have been transformed using an exponential transformation to interpret them as a percentage change.},
remark{Source} = {Eurovoices General Population Poll 2024},
]
{                     
colspec={Q[l]Q[l]Q[c]Q[c]Q[c]Q[c]Q[c]},
colsep=4pt
}
\toprule
I. Divergence & Pol. Alignment & Estimate & $Pr(>|z|)$ & 95\% CI Lower & 95\% CI Upper & Visualization \\
\midrule
Low & Non-Incumbent & \num{ -0.180}*** & 0.000 & -0.209 & -0.149 & \includegraphics[width=0.47in, height=0.12in]{"viz/heteffects_dissonance_1.png"}\\
 & Incumbent & \num{-0.085} & 0.000 & -0.168 & 0.006 & \includegraphics[width=0.47in, height=0.12in]{"viz/heteffects_dissonance_2.png"}\\
High & Non-Incumbent & \num{-0.211}*** & 0.000 & -0.238 & -0.183 & \includegraphics[width=0.47in, height=0.12in]{"viz/heteffects_dissonance_3.png"}\\
 & Incumbent & \num{-0.179}*** & 0.000 & -0.241 & -0.111 & \includegraphics[width=0.47in, height=0.12in]{"viz/heteffects_dissonance_4.png"}\\
\bottomrule
\end{talltblr}
\end{table}
